A Neural, Parallel Theorem Prover*

### 2019-05-13 papers/FroCoS19/paper.tex
self citation yay

\section{Introduction}
Recent advances~ in neural network systems allow for processing graph-structured data in a neural context.
Graphs are a natural representation for logical formulae as found in automatic theorem provers (ATPs), suggesting a new breed of \emph{neural ATP} in which proof search is guided by a neural black-box acting as ``mathematician's intuition''.
However, in practice there are several implementation issues which must be avoided in order for neural systems to integrate with efficient traditional ATPs:
\begin{enumerate}
	\item Proof state in such systems may be very large, such as in saturation-based provers, leading to training data which is impractical to learn from and slow to evaluate.
	\item Data structures employed may be very opaque or ``unnatural'', containing artifice designed for efficiency rather than natural comprehension by a neural network.
	\item Systems may be very sensitive to latency, which can result in the introduction of neural guidance systems crippling prover throughput and hence performance.
\end{enumerate}
%
Attempting to solve these issues with a novel prover architecture, and exploring several options to improve overall efficiency, the prototype system \lerna{}\footnote{\textbf{Le}arning to \textbf{R}eason with \textbf{N}eural \textbf{A}rchitectures. Lerna is also the lair of the mythical many-headed beast \textsc{Hydra}.} takes an alternative step toward useful neural automatic theorem provers.

>>>>

\section{Introduction}
Recent advances~ in neural network systems allow for processing graph-structured data in a neural context.
Graphs are a natural representation for logical formulae as found in automatic theorem provers (ATPs), suggesting a new breed of \emph{neural ATP} in which proof search is guided by a neural black-box acting as ``mathematician's intuition''.
However, in practice there are several implementation issues~\cite{lerna-discussion} which must be avoided in order for neural systems to integrate with efficient traditional ATPs:
\begin{enumerate}
	\item Proof state in such systems may be very large, such as in saturation-based provers, leading to training data which is impractical to learn from and slow to evaluate.
	\item Data structures employed may be very opaque or ``unnatural'', containing artifice designed for efficiency rather than natural comprehension by a neural network.
	\item Systems may be very sensitive to latency, which can result in the introduction of neural guidance systems crippling prover throughput and hence performance.
\end{enumerate}
%
Attempting to solve these issues with a novel prover architecture, and exploring several options to improve overall efficiency, the prototype system \lerna{}\footnote{\textbf{Le}arning to \textbf{R}eason with \textbf{N}eural \textbf{A}rchitectures. Lerna is also the lair of the mythical many-headed beast \textsc{Hydra}.} takes an alternative step toward useful neural automatic theorem provers.
